Conservation of interaction partners between related plants varies widely across communities and between plant families - Supporting Information

### 2019-07-30 manuscript/phylogenetic_signal_manuscript.tex
small catches
changing Inger-Marie's name, minor typos

\author{Alyssa R. Cirtwill$^{1,2}$, Giulio V. Dalla Riva$^{3}$, Nick J. Baker$^{1}$,\\
Mikael Ohlsson$^{4}$, Isabelle Norstr\"{o}m$^{4}$, Inger-Marie Wohlfarth Hasle$^{4}$,\\
Joshua A. Thia$^{1,5}$, 
% Christie J. Webber$^{1}$, % Christie has confirmed that she'd rather be in the acknowledgements than an author
Daniel B. Stouffer$^{1}$}
\date{\small$^1$Centre for Integrative Ecology, School of Biological Sciences\\University of Canterbury\\Private Bag 4800\\
Christchurch 8140, New Zealand\\
\medskip$^2$Present address: Department of Ecology,\\
Environment, and Plant Sciences (DEEP)\\
Stockholm University\\
114 19 Stockholm, Sweden\\
\medskip$^3$Biomathematics Research Centre, School of Mathematics and Statistics\\
University of Canterbury\\Private Bag 4800\\
Christchurch 8140, New Zealand\\
\medskip$^4$Department of Physics, Chemistry, and Biology (IFM)\\ Link\"{o}ping University\\ 581 83 Link\"{o}ping, Sweden\\
\medskip$^5$Present Address: School of Biological Sciences\\
The University of Queensland\\Brisbane, QLD 4072, Australia }

@@

    We calculated niche overlap for each pair of species within a community 
    using a Jaccard index to describe the number of shared interaction 
    partners, augmented with the number of interaction partners which were 
    not shared. The Jaccard index $J_{ij}$ describes the proportion of 
    shared interaction partners for for species $i$ and $j$ and is defined as: 
  %
    \begin{equation}
      J_{ij} = \frac{M_{ij}}{P_i+P_j-M_{ij}} ,
    \end{equation}
  %
    where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners of 
    species $i$ and $j$ and $P_i$ and $P_j$ are the sizes of the sets of interaction 
    \emph{partners} for species $i$ and $j$ respectively. We wished to give more 
    weight to species sharing a large number of interaction partners as well as 
    those sharing a large proportion (i.e., to emphasize pairs of generalists 
    sharing most of their interaction partners over specialists sharing a single 
    interaction partner). Note that species sharing a large \emph{number} of interaction partners may not share a large \emph{proportion} of interaction partners if the number of interaction partners that are not shared is also large. % Added because Josh got confused about the distinction.
    To capture all of this information for each species pair, we therefore recorded the number of 
    shared interaction partners ($M_{ij}$) and the number of interaction partners 
    that were not shared 
    ($U_{ij}$ = $P_{i}$+$P_{j}$-2$M_{ij}$). Instead of a single index $J_{ij}$, 
    we thus kept track of the full information needed to compute
    niche overlap between species $i$ and $j$ as a tuple: ($M_{ij}$, $U_{ij}$).

@@

  ARC, DBS, GVDR, and NJB designed the research. ARC, MO, IN, and IMWH, JAT, and CJW collected published data. 
  ARC and GVDR performed the analyses. All authors contributed to the manuscript.

>>>>

\author{Alyssa R. Cirtwill$^{1,2}$, Giulio V. Dalla Riva$^{3}$, Nick J. Baker$^{1}$,\\
Mikael Ohlsson$^{4}$, Isabelle Norstr\"{o}m$^{4}$, Inger-Marie Wohlfarth$^{4}$,\\ % All confirmed to submit
Joshua A. Thia$^{1,5}$, % Confirmed to submit
% Christie J. Webber$^{1}$, % Christie has confirmed that she'd rather be in the acknowledgements than an author
Daniel B. Stouffer$^{1}$}
\date{\small$^1$Centre for Integrative Ecology, School of Biological Sciences\\University of Canterbury\\Private Bag 4800\\
Christchurch 8140, New Zealand\\
\medskip$^2$Present address: Department of Ecology,\\
Environment, and Plant Sciences (DEEP)\\
Stockholm University\\
114 19 Stockholm, Sweden\\
\medskip$^3$Biomathematics Research Centre, School of Mathematics and Statistics\\
University of Canterbury\\Private Bag 4800\\
Christchurch 8140, New Zealand\\
\medskip$^4$Department of Physics, Chemistry, and Biology (IFM)\\ Link\"{o}ping University\\ 581 83 Link\"{o}ping, Sweden\\
\medskip$^5$Present Address: School of Biological Sciences\\
The University of Queensland\\Brisbane, QLD 4072, Australia }

@@

    We calculated niche overlap for each pair of species within a community 
    using a Jaccard index to describe the number of shared interaction 
    partners, augmented with the number of interaction partners which were 
    not shared. The Jaccard index $J_{ij}$ describes the proportion of 
    shared interaction partners for species $i$ and $j$ and is defined as: 
  %
    \begin{equation}
      J_{ij} = \frac{M_{ij}}{P_i+P_j-M_{ij}} ,
    \end{equation}
  %
    where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners of 
    species $i$ and $j$ and $P_i$ and $P_j$ are the sizes of the sets of interaction 
    \emph{partners} for species $i$ and $j$ respectively. We wished to give more 
    weight to species sharing a large number of interaction partners as well as 
    those sharing a large proportion (i.e., to emphasize pairs of generalists 
    sharing most of their interaction partners over specialists sharing a single 
    interaction partner). Note that species sharing a large \emph{number} of interaction partners may not share a large \emph{proportion} of interaction partners if the number of interaction partners that are not shared is also large. % Added because Josh got confused about the distinction.
    To capture all of this information for each species pair, we therefore recorded the number of 
    shared interaction partners ($M_{ij}$) and the number of interaction partners 
    that were not shared 
    ($U_{ij}$ = $P_{i}$+$P_{j}$-2$M_{ij}$). Instead of a single index $J_{ij}$, 
    we thus kept track of the full information needed to compute
    niche overlap between species $i$ and $j$ as a tuple: ($M_{ij}$, $U_{ij}$).

@@

  ARC, DBS, GVDR, and NJB designed the research. ARC, MO, IN, and IMW, JAT, and CJW collected published data. 
  ARC and GVDR performed the analyses. All authors contributed to the manuscript.

### 2019-07-30 manuscript/supporting_info.tex
increased size of Fig. S2
trimmed summary to fit word limit, small formatting tweaks
older changes
small catches from Micke
changing Inger-Marie's name, minor typos

\author{Alyssa R. Cirtwill$^{1,2}$, Giulio V. Dalla Riva$^{3}$, Nick J. Baker$^{1}$,\\
Mikael Ohlsson$^{4}$, Isabelle Norstr\"{o}m$^{4}$, Inger-Marie Wohlfarth Hasle$^{4}$,\\
Joshua A. Thia$^{1,5}$, Christie J. Webber$^{1}$, Daniel B. Stouffer$^{1}$}
\date{\small$^1$Centre for Integrative Ecology, School of Biological Sciences\\
\medskip$^2$Department of Ecology,\\
Environment, and Plant Sciences (DEEP)\\
Stockholm University\\
114 19 Stockholm, Sweden\\
\medskip$^3$Biomathematics Research Centre, School of Mathematics and Statistics\\
University of Canterbury\\Private Bag 4800\\
Christchurch 8140, New Zealand\\
\medskip$^4$Department of Physics, Chemistry, and Biology (IFM)\\ Link\"{o}ping University\\ 581 83 Link\"{o}ping, Sweden\\
\medskip$^5$Present Address: School of Biological Sciences\\
University of Queensland\\Brisbane, QLD 4072, Australia }

\begin{document}
\maketitle
\baselineskip=8.5mm
\begin{spacing}{1.0}

\beginsupplement
\clearpage

@@

    \begin{figure}[!h]
        \begin{center}
          \centerline{\includegraphics*[width=.75\textwidth]{Figures/random_p_distributions.eps}}
        \end{center}
         \caption{\small Nearly uniform distributions of $p$-values where obtained when comparing the strength of the relationship between niche overlap and phylogenetic distance in 999 permutations of each network in our dataset with 500 permutations of each permuted network. Each line in each panel represents the histogram of $p$-values for one network. Bins are 0.1 wide. Purple lines in panels A-L represent pollination networks while green lines in panels M-N represent plant-herbivore networks. A list of networks shown on each panel follows; see Table S1 for original sources.
         % Networks are as follows (darkest to lightest): \textbf{A)} M\_PL\_001, M\_PL\_002, M\_PL\_003, M\_PL\_004, M\_PL\_005;      \textbf{B)} M\_PL\_006, M\_PL\_007, M\_PL\_008, M\_PL\_009, M\_PL\_010;      \textbf{C)} M\_PL\_011, M\_PL\_012, M\_PL\_013, M\_PL\_014, M\_PL\_015;      \textbf{D)} M\_PL\_016, M\_PL\_017, M\_PL\_018, M\_PL\_019, M\_PL\_020;      \textbf{E)} M\_PL\_021, M\_PL\_022, M\_PL\_023, M\_PL\_024, M\_PL\_025;   \textbf{F)} M\_PL\_026, M\_PL\_027, M\_PL\_028, M\_PL\_029, M\_PL\_030;     \textbf{G)} M\_PL\_031, M\_PL\_032, M\_PL\_033, M\_PL\_034, M\_PL\_035;   \textbf{H)} M\_PL\_036, M\_PL\_037, M\_PL\_038, M\_PL\_039, M\_PL\_040;     \textbf{I)} M\_PL\_041, M\_PL\_042, M\_PL\_043, M\_PL\_044, M\_PL\_045; \textbf{J)} M\_PL\_046, M\_PL\_047, M\_PL\_048, M\_PL\_049, M\_PL\_050;      \textbf{K)} M\_PL\_051, M\_PL\_052, M\_PL\_053, M\_PL\_054, M\_PL\_055;     \textbf{L)} M\_PL\_056, M\_PL\_057, M\_PL\_058, M\_PL\_059;      \textbf{M)} Ibanez, Joern\_altuda, Joern\_marathon, Peralta, Sheldon;      \textbf{N)} Ueckert, Basset, Bluthgen, Bodner, Coley, Novotny.     For original sources for each network, see Table S1.
         }
        \label{within_family_regression}
      \end{figure}

>>>>

\author{Alyssa R. Cirtwill$^{1,2}$, Giulio V. Dalla Riva$^{3}$, Nick J. Baker$^{1}$,\\
Mikael Ohlsson$^{4}$, Isabelle Norstr\"{o}m$^{4}$, Inger-Marie Wohlfarth$^{4}$,\\
Joshua A. Thia$^{1,5}$, 
% Christie J. Webber$^{1}$, 
Daniel B. Stouffer$^{1}$}
\date{\small$^1$Centre for Integrative Ecology, School of Biological Sciences\\
\medskip$^2$Department of Ecology,\\
Environment, and Plant Sciences (DEEP)\\
Stockholm University\\
114 19 Stockholm, Sweden\\
\medskip$^3$Biomathematics Research Centre, School of Mathematics and Statistics\\
University of Canterbury\\Private Bag 4800\\
Christchurch 8140, New Zealand\\
\medskip$^4$Department of Physics, Chemistry, and Biology (IFM)\\ Link\"{o}ping University\\ 581 83 Link\"{o}ping, Sweden\\
\medskip$^5$Present Address: School of Biological Sciences\\
The University of Queensland\\Brisbane, QLD 4072, Australia }

\begin{document}
\maketitle
\baselineskip=8.5mm
\begin{spacing}{1.5}

\linenumbers
\beginsupplement
\clearpage

@@

    \begin{figure}[!h]
        \begin{center}
          \centerline{\includegraphics*[width=.99\textwidth]{Figures/random_p_distributions.eps}}
        \end{center}
        \vspace{-1cm}
         \caption{\small Nearly uniform distributions of $p$-values where obtained when comparing the strength of the relationship between niche overlap and phylogenetic distance in 999 permutations of each network in our dataset with 500 permutations of each permuted network. Each line in each panel represents the histogram of $p$-values for one network. Bins are 0.1 wide. Purple lines in panels A-L represent pollination networks while green lines in panels M-N represent plant-herbivore networks. A list of networks shown on each panel follows; see Table S1 for original sources.
         % Networks are as follows (darkest to lightest): \textbf{A)} M\_PL\_001, M\_PL\_002, M\_PL\_003, M\_PL\_004, M\_PL\_005;      \textbf{B)} M\_PL\_006, M\_PL\_007, M\_PL\_008, M\_PL\_009, M\_PL\_010;      \textbf{C)} M\_PL\_011, M\_PL\_012, M\_PL\_013, M\_PL\_014, M\_PL\_015;      \textbf{D)} M\_PL\_016, M\_PL\_017, M\_PL\_018, M\_PL\_019, M\_PL\_020;      \textbf{E)} M\_PL\_021, M\_PL\_022, M\_PL\_023, M\_PL\_024, M\_PL\_025;   \textbf{F)} M\_PL\_026, M\_PL\_027, M\_PL\_028, M\_PL\_029, M\_PL\_030;     \textbf{G)} M\_PL\_031, M\_PL\_032, M\_PL\_033, M\_PL\_034, M\_PL\_035;   \textbf{H)} M\_PL\_036, M\_PL\_037, M\_PL\_038, M\_PL\_039, M\_PL\_040;     \textbf{I)} M\_PL\_041, M\_PL\_042, M\_PL\_043, M\_PL\_044, M\_PL\_045; \textbf{J)} M\_PL\_046, M\_PL\_047, M\_PL\_048, M\_PL\_049, M\_PL\_050;      \textbf{K)} M\_PL\_051, M\_PL\_052, M\_PL\_053, M\_PL\_054, M\_PL\_055;     \textbf{L)} M\_PL\_056, M\_PL\_057, M\_PL\_058, M\_PL\_059;      \textbf{M)} Ibanez, Joern\_altuda, Joern\_marathon, Peralta, Sheldon;      \textbf{N)} Ueckert, Basset, Bluthgen, Bodner, Coley, Novotny.     For original sources for each network, see Table S1.
         }
        \label{within_family_regression}
      \end{figure}
